Data Structures Comparative Review Thing

### 2014-04-17 paper/paper.tex
Wrote the conclusion and reflection

    The skip list uses the least memory but is awful in every other imaginable way.  The hashmap is
    usually the best, except when we're dealing with a small number of integer keys and doing far more
    inserts than queries.  Note that this doesn't actually happen in practice.

>>>>

    Our secondary point of research encompassed the effect of key complexity on associative data structures.
    Our different types of keys were IP adresses, domain names and full path URLs. We have seen that as expected,
    IP adresses as keys give a significant speedup over the other two, and use less memory as well. Interesting to
    note is that we found the only advantage of the binary search tree over the hashmap here, in that insertions of
    a small amount of IP adresses, up to around $2^13$ insertions, is faster. So when writing an application with very
    few keys of low complexity, with more insertions than queries, the binary search tree may be the best option. Lastly,
    we have found that the domain key type does not outperform the full path key type. It is not significantly better
    if it is better at all.
    %The skip list uses the least memory but is awful in every other imaginable way.  The hashmap is
    %usually the best, except when we're dealing with a small number of integer keys and doing far more
    %inserts than queries.  Note that this doesn't actually happen in practice.

    \section{Reflection}
    In general, we are glad with the results of our research. We were able to provide clear and concise answers to our
    research questions. Even though our research questions may appear broad, we have defined a good scope in our research
    proposal and have virtually not mended this scope in our research. One small change is that we also included datasets of
    size $2^8$ because we saw some interesting results in very small sets. In our implementation we have changed quite a few
    things because we ran into pratical problems. Some of these required us to change the allocator and generate our keys
    in a slightly different fashion, which we all documented in this paper.

    Since we have found that the hash map is the best associative data structure overal for this problem, we might do further
    research in different kind of hash maps. We might try different hash functions, different methods of collision resolution,
    and perhaps survey different kinds of concurrent hash maps.
